Do moral communities have a spatial dimension? A spatial exploratory analysis of places of worship and violent crime in the city of Recife, Brazil

### 2019-10-15 Moral_Communities_and_Crime_v1.tex
Completed first draft of analysis/results and conclusions.

Yet another fruitful avenue for research, and one that has only recently
begun to be explored, is the presence of environmental attributes that
can help to reinforce moral norms, such as schools and churches (e.g.,
Abdullah et al. 2018; Davignon and Thomson 2015; Furr-Holden et al.
2010; Traunmuller 2011). It is thus that in a recent paper, Warner and
Konkel (2019) note that the role of places of worship, as distinct
entities from the members of the congregations, have received less
attention in empirical and theoretical research for their deterrence
potential. The role of these institutions might be particularly
important in places where formal state institutions lack the means or
the will to enforce norms - as is the case in Brazil.

@@

For the analysis, we use Principal Component Analysis, a data reduction
technique, to obtain an indicator of Socio-Economic Deprivation. The
loadings of the first factor, which accounts for almost 54\% of the
variance, are shown in Table \ref{tab:sed-descriptive-statistics}. The
loadings of this factor indicate that high Socio-Economic Deprivation is
a combination of (in terms of importance): high levels of poverty, high
levels of unemployment, and low median income, followed by high levels
of family disruption, in particular proportion of families led by young
single mothers.

@@

\caption{\label{tab:table-sed-descriptive-statistics}\label{tab:sed-descriptive-statistics}Descriptive statistics of some key socio-economic and demographic variables in Recife}
\centering
\begin{tabular}[t]{lrrrrrrr}
\toprule
Variable & Min & 2nd Quartile & Median & Mean & 3rd Quartile & Max & \makecell[l]{PC Factor 1\\ Loadings}\\
\midrule
Median Income & 122.05 & 337.40 & 581.67 & 1031.09 & 1283.79 & 7954.19 & -0.42\\
Proportion Unemployed & 0.00 & 0.05 & 0.10 & 0.10 & 0.14 & 0.59 & 0.56\\
Proportion Poverty & 0.00 & 0.05 & 0.11 & 0.12 & 0.17 & 0.63 & 0.58\\
Proportion Single Mother & 0.00 & 0.33 & 0.37 & 0.37 & 0.41 & 0.70 & 0.17\\
Proportion Young Single Mother & 0.00 & 0.01 & 0.02 & 0.02 & 0.02 & 0.21 & 0.38\\
\bottomrule
\multicolumn{8}{l}{\textit{Note: }}\\
\multicolumn{8}{l}{The variable for young single mothers is for women aged 15-25}\\
\multicolumn{8}{l}{The first principal component accounts for 53.91\% of the variance}\\
\end{tabular}
\end{table}

Figure \ref{fig:plot-sed-as-quintiles} displays the geography of
Socio-Economic Deprivation in Recife, after classifying \emph{setores}
by quintiles, whereby the ``High'' class corresponds to \emph{setores}
in the top 20\% of the Socio-Economic Deprivation indicator, and the
``Low'' class corresponds to \emph{setores} in the bottom 20\% of the
Socio-Economic Deprivation indicator. The figure shows a veritable
mosaic of affluence and deprivation, with high deprivation areas
directly in contact, and in some cases even completely surrounded, by
low deprivation areas. This geographical pattern of unequality, on the
other hand, seems to be characteristic of Brazilian metropolitan
regions, where enclaves of wealth and \emph{favelas} (i.e., urban slums)
can be found in close proximity (see for example Feitosa et al. 2007).

@@

Calculate the intensity of other ppp by quadrat:

@@

@@

@@

@@

@@

An opposing viewpoint is offered by the theory of conservative
Protestants (Ellison, Burr, and McCall 2003). This theory argues that
religion is not always beneficial in order to guarantee social order,
and consequently to result in lower crime rates. This theory suggested
that, conservative Protestants are more tolerate with violent behavior
when associated with defense of honor, family, property, or woman.
However, high rates are not expected for all types of crimes in densely
populated areas of conservative Protestants. But what justifies this
behavior? Ellison et al.~(2003) argue that this tolerance stems from a
religious view of the world. More clearly, punishment is seen as a
legitimate form of retribution whose explanation can be attributed to
the literal interpretation of the Bible. In the specific context of
Brazil, it is important to consider that the interpretations and
meanings attributed to urban violence during the last two decades in
Brazil often had religious figures as protagonists (Birman and Machado
2012).

@@

The theory of conservative Protestants, argues that conservative
Protestants are more likely to tolerate violent behavior of a defensive
or punitive character, especially when associated to defense of honor,
family, property, or woman. Our objective in the study is to explore the
question whether moral communities have a spatial dimension. To this end
we deploy an array of spatial analytical tools to investigate potential
patterns of clustering of violent crime and places of worship, using as
well other kinds of urban facilities to act as controls. The case study
is the city of Recife, in the northeast of Brazil, and analysis is based
on geographically detailed datasets of criminal events as well as
several types of urban facilities.

@@

\leavevmode\hypertarget{ref-Birman2012violencia}{}%
Birman, Patricia, and Carly Machado. 2012. ``A Violencia Dos Justos:
Evangelicos, Midia E Periferias Da Metropole.'' \emph{Revista Brasileira
de Ciências Sociais} 27 (80): 55--69.

@@

\leavevmode\hypertarget{ref-Ellison2003enduring}{}%
Ellison, Christopher G, Jeffrey A Burr, and Patricia L McCall. 2003.
``The Enduring Puzzle of Southern Homicide: Is Regional Religious
Culture the Missing Piece?'' \emph{Homicide Studies} 7 (4): 326--52.

@@

@@

@@

@@

@@

>>>>

Yet another fruitful avenue for research, and one that has only recently
begun to be explored, is the presence of environmental attributes that
can help to reinforce moral norms, such as schools and churches (e.g.,
Abdullah et al. 2018; Davignon and Thomson 2015; Furr-Holden et al.
2010; Traunmuller 2011). It is thus that in a recent paper, Warner and
Konkel (2019) note that the role of places of worship, as distinct
entities from the members of the congregations, have received less
attention in empirical and theoretical research for their deterrence
potential. The role of these institutions might be particularly
important in places where formal state institutions lack the means or
the will to enforce norms in a consistent way - as is the case in Brazil
(Garmany 2014).

@@

For the analysis, we use Principal Component Analysis, a data reduction
technique, to obtain an indicator of Socio-Economic Deprivation,
essentially the first principal component in the output. The loadings of
this factor (Table \ref{tab:sed-descriptive-statistics}) indicate that
high Socio-Economic Deprivation is a combination of (in terms of
importance): high levels of poverty, high levels of unemployment, and
low median income, followed by high levels of family disruption, in
particular proportion of families led by young single mothers. This
factor accounts for almost 54\% of the variance..

@@

\caption{\label{tab:table-sed-descriptive-statistics}\label{tab:sed-descriptive-statistics}Descriptive statistics of some key socio-economic and demographic variables in Recife}
\centering
\begin{tabular}[t]{lccccccc}
\toprule
Variable & Min & 2nd Quartile & Median & Mean & 3rd Quartile & Max & \makecell[l]{PC Factor 1\\ Loadings}\\
\midrule
Median Income & 122.05 & 337.40 & 581.67 & 1031.09 & 1283.79 & 7954.19 & -0.42\\
Proportion Unemployed & 0.00 & 0.05 & 0.10 & 0.10 & 0.14 & 0.59 & 0.56\\
Proportion Poverty & 0.00 & 0.05 & 0.11 & 0.12 & 0.17 & 0.63 & 0.58\\
Proportion Single Mother & 0.00 & 0.33 & 0.37 & 0.37 & 0.41 & 0.70 & 0.17\\
Proportion Young Single Mother & 0.00 & 0.01 & 0.02 & 0.02 & 0.02 & 0.21 & 0.38\\
\bottomrule
\multicolumn{8}{l}{\textit{Note: }}\\
\multicolumn{8}{l}{The variable for young single mothers is for women aged 15-25}\\
\multicolumn{8}{l}{The first principal component accounts for 53.91\% of the variance}\\
\end{tabular}
\end{table}

Figure \ref{fig:plot-sed-as-quintiles} displays the geography of
Socio-Economic Deprivation in Recife, after classifying \emph{setores}
by quintiles, whereby the ``High'' class corresponds to \emph{setores}
in the top 20\% of the Socio-Economic Deprivation indicator, and the
``Low'' class corresponds to \emph{setores} in the bottom 20\% of the
Socio-Economic Deprivation indicator. The figure shows a veritable
mosaic of affluence and deprivation, with high deprivation areas
directly in contact, and in some cases almost completely surrounded, by
low deprivation areas. This geographical pattern of unequality, on the
other hand, seems to be characteristic of Brazilian metropolitan
regions, where enclaves of wealth and \emph{favelas} (i.e., urban slums)
can be found in close proximity (see for example Feitosa et al. 2007).

@@

Once the indicator of Socio-Economic Deprivation has been obtained, as
outlined above, it can be used for conditional quadrat analysis. As
previously described, the quadrats are irregular areas that are defined
based on a covariate, in this case the quintiles of the Socio-Economic
Deprivation indicator. In essence, this entails counting the number of
events at each level of the covariate, and then calculating an estimator
of the intensity.

Figure \ref{fig:plot-crime-quadrat} shows the results of conditional
quadrat counts for Lethal and Intentional Violent Crime. The dotted line
indicates the global intensity, simply the total number of criminal
events divided by the area of the region. It can be seen that the
intensity of crime clearly increases with Socio-Economic Deprivation,
and the intensity in areas with the highest levels of Socio-Economic
Deprivation is 208.7065292 \% higher than in places with the lowest
levels of Socio-Economic Deprivation. This is as expected, as research
has consistently found correlations between Socio-Economic Deprivation
and a variety of negative health outcomes, including homicide (Ichihara
et al. 2018). A \(\chi^2\) test of independence on the quadrat counts
yields a value of \(p\leq 0.0001\) (four degrees of freedom), which
comfortably rejects the null hypothesis of homogeneity of intensity of
crime by level of Socio-Economic Deprivation.

@@

Next, we repeat the analysis of conditional quadrat counts, but now for
the six types of events of reference. As discussed above, this included
three types of places of worship which are of interest from the
perspective of moral communities, and three types of commercial
establishments that we posit are morally neutral. The results of
estimating the intensity of the process by means of conditional quadrat
counts are shown in Figure \ref{fig:plot-events-quadrat}.

The first thing that we note are the variations in global intensity of
places of worship, with Evangelical places of worship being the most
intense of the three. There are no clear variations in the locational
pattern of Catholic places of worship by level of Socio-Economic
Deprivation. Evangelical places of worship, on the other hand, tend to
be found more frequently in places with middle-low and middle levels of
Socio-Economic Deprivation, a pattern also discernible, albeit barely,
for Spiritist churches. Interestingly (see Table
\ref{tab:quadrat-test-statistics}) \(\chi^2\) tests of independence on
the conditional quadrat counts fail to reject the hypothesis of
homogeneity for Catholic and Spiritist churches, and it is only in the
case of Evangelical places of worship that we detect the possibility of
locational patterns that vary by level of Socio-Economic Deprivation.

Three types of commercial establishments also appear to display
inhomogeneous locational patterns (Table
\ref{tab:quadrat-test-statistics}), with the \(\chi^2\) test of
independence emphaticaly rejecting the null hypothesis. As seen in
Figure \ref{fig:plot-events-quadrat}, ice cream shops tend to be found
more frequently in places with middle-low Socio-Economic Deprivation,
and less frequently in places with middle-high Socio-Economic
Deprivation. Pharmacies show a clearer trend, with locational patterns
that tend to favor places with low Socio-Economic Deprivation. Finally,
supermarkets are found less frequently in places with middle-high and
high Socio-Economic Deprivation.

@@

\caption{\label{tab:table-quadrat-test-statistics}\label{tab:quadrat-test-statistics}$\chi^2$ tests of independence of conditional quadrat counts}
\centering
\begin{tabular}[t]{lccc}
\toprule
Event & Statistic & Degrees of Freedom & p-value\\
\midrule
Catholic & 6.913 & 4 & 0.2811\\
Evangelical & 38.669 & 4 & $<0.001$\\
Spiritist & 9.108 & 4 & 0.1169\\
Ice Crem Shop & 15.108 & 4 & 0.009\\
Pharmacy & 51.869 & 4 & $<0.001$\\
\addlinespace
Supermarket & 23.826 & 4 & $<0.001$\\
\bottomrule
\end{tabular}
\end{table}

@@

The preceding analysis provides a valuable backdrop. As seen there,
there is a clear distribution of criminal events, increasing on par with
the level of Socio-Economic deprivation. Of the three different classes
of places of worship, only Evangelical churches display a locational
pattern that is commensurate, with Socio-Economic Deprivation, albeit
the pattern is distinct from criminal events, with Evangelical churches
found less frequently in both high and low Socio-Economic Deprivation
areas.

The analysis does not answer the question, yet, of possible covariations
between crime, on the one hand, and places of worship and commercial
establishments, on the other. In this subsection we implement the
relative distribution estimator of intensity of Lethal and Intentional
Violent Crime. The covariate \(Z(u)\) in this analysis is distance to
one of a place of worship or a commercial establishment: \[
\lambda_k(s)=\rho(Z_k(s))
\] with: \[
Z_k(s) = d_{sk}
\] In the expression above, \(d_{s_k}\) is distance from location \(s\)
to an event of class \(k\), and
\(k=\{\text{Catholic, Evangelical, Spiritist, Ice Cream Shop, Pharmacy, Supermarket}\}\).

The results of this analysis are shown in Figure
\ref{fig:plot-relative-distribution}. The global estimator for the
intensity of crime is shown in this figure as a dotted line. Three types
of places of worship are shown in solid lines, and three types of
commercial establishments are shown in dashed lines. Each relative
distribution function is shown with its corresponding 95\% confidence
bands.

Several interesting things emerge from inspection of this figure. First,
we notice that with the exception of Spiritist churches (which has an
intensity significantly lower than the global intensity at a distance of
zero), the intensity of crime at for other churches and commercial
establishments is close, but higher than, the global intensity of crime.
In general, the intensity tends to increase at short distances; however,
this effect is much more marked for Evangelical places of worship. The
intensity of crime in the proximity of these places of worship grows
rapidly within a short distance, reaching a peak of
\ensuremath{2.4916\times 10^{-5}} at a distance of 64.92 m. At that
distance, the intensity of crime with respect to Evangelical places of
worship is 183.78\% higher than the intensity of Catholic places of
worship; 194.54\% higher than the intensity of crime with respect to
Spiritist churches; 174.19\% higher than the intensity with respect to
ice cream shops; 151.52\% higher than the intensity with respect to
pharmacies; and 177.63\% higher than the intensity with respect to
supermarkets.

Intriguingly, after reaching its peak intensity, the intensity of crime
with respect to Evangelical places of worship declines sharply, until at
distances of approximately 200 m it is lower than for other places of
worship and commercial establishments, and at distances of approximately
270 m it is lower than the global intensity of crime. This does not
happen with other places of worship or commercial establishments: the
intensity of crime with respect to these locations remains higher than
the global intensity of crime for the interval of distances examined.
Another interesting observation is that the intensity of crime with
respect to Catholic places of worship is not substantially different
when compared to the intensity of crime with respect to any of the
commercial establishments considered.

These results, while intriguing, beg the question of whether variations
in Socio-Economic Deprivation may have a confounding effect on the
relative distributions; for instance, if as seen in the case of
conditional quadrat counts, there is some overlap in the locational
patterns of, say, Evangelical places of worship and crime with respect
to Socio-Economic Deprivation. Next section explores this question.

\begin{figure}
\centering
\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/figure-plot-relative-distribution-1.pdf}
\caption{\label{fig:plot-relative-distribution}Intensity of crime as a
function of distance to a selected place of worship or commercial
establishment; bands are 95\% confidence interval and the dotted line
indicates the global intensity of crime}
\end{figure}

@@

In this section, the preceding analysis regarding the relative
distribution of crime using distance to places of worship and commercial
establishments is repeated, after introducing a baseline function. The
interpretation of \(\rho(Z(s))\) in this case is as follows: instead of
the raw intensity at the value of \(z\), it is the intensity
\emph{relative to the intensity according to the level of Socio-Economic
Deprivation}. Therefore, \(rho(z)=1\) matches the intensity according to
Socio-Economic Deprivation; values of \(rho(z)>1\) indicate a higher
intensity than explained by Socio-Economic Deprivation; and values of
\(rho(z)<1\) correspond to lower intensities than explained by
Socio-Economic Deprivation.

The results of the analysis are shown in Figure
\ref{fig:plot-relative-distribution-with-baseline}. The general trends
shown by the relative distribution functions are similar to those seen
above, before the introduction of a baseline function. We notice that at
short distances the intensity of crime as a function of distance to the
various places of worship and commercial establishments is higher than
the baseline intesity (i.e., the intensity according to Socio-Ecomomic
Deprivation). The only exception is intensity as a function of distance
to a Spiritist church, which at short distances is not significantly
different from the baseline intensity (see the confidence bands).

The peak intensity as a function of distance to Evangelical churches is
3.33 times the baseline intensity; for Catholic places of worship, the
highest intesity is 2.12 times the baseline intensity; and the intensity
reaches a peak of 2.67 times the baseline intensity when the covariate
is distance to Spiritist churches. Turning now to inspect the three
types of commercial establishments, we see that the highest intensities
are 2.28, 2.46, and 2.09 times the intensity according to Socio-Economic
Deprivation for ice cream shops, pharmacies, and supermarkets,
respectively.

Some differences are observed as well. Whereas the peak intensity as a
function of distance to Evangelical places of worship was 183.78\%
higher than the intensity of Catholic places of worship \emph{without a
baseline function}, once that we account for Socio-Economic Deprivation
by means of a baseline function, the peak relative intensity as a
function of distance to Evangelical churches declines to 176.53\% higher
than the intensity as a function of distance to Catholic places of
worship at the same distance. Accounting for Socio-Economic Deprivation
in this analysis of intensity has in general a moderating effect:
whereas the peak intensity of crime was was 194.54\% higher when
comparing Evangelical and Spiritist churches at the distance of the peak
intensity of Evangelical churches, this difference declines to 186.45\%
after accounting for Socio-Economic Deprivation. Similarly, this changes
from 174.19\% to 168.33\% in the case of ice cream shops, from 151.52\%
to 140.97\% in the case of pharmacies, and finally from 177.63\% to
164.33\% in the case of supermarkets.

Again, it is interesting to note that while the intensity with respect
to distance to Catholic and Spiritist places of worship, as well as ice
cream shops, pharmacies, and supermarkets remains higher than the
background intensity (given by the baseline according to Socio-Economic
Deprivation), the intensity of crime at distances of approximately 300 m
of an Evangelical church are significantly lower than the background
intensity of crime. In the following section we discuss the possible
implications of these findings.

\begin{figure}
\centering
\includegraphics{Moral_Communities_and_Crime_v1_files/figure-latex/figure-plot-relative-distribution-with-baseline-1.pdf}
\caption{\label{fig:plot-relative-distribution-with-baseline}Intensity
of crime as a function of distance to a selected place of worship or
commercial establishment after introducing Socio-Economic Deprivation as
a baseline function; bands are 95\% confidence intervals and the dotted
line indicates the baseline intensity with respect to Socio-Economic
Deprivation}
\end{figure}

@@

Words go here.

@@

The objective of this research was to investigate the covariation of
incidence of crime to proximity of places of worship. The hypothesis of
moral communities (closely related to social disorganization theory)
posits that a negative correlation between the presence of churches and
crime. Recent papers have argued that it is important to study this
phenomenon from a geographical perspective, paying attention to the
level of aggregation. Accordingly, our research for the city of Recife
in Brazil makes the following contributions to the literature:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  By using disaggregated data for Lethal and Intentional Violent Crime
  and various types of places of worship, we were able to analyze the
  intensity of crime with respect to proximity to churches as a point
  pattern.
\item
  Following the suggestion of Warner and Konkel (2019), we also
  disaggregate our data by type of place of worship, and consider the
  three following denominations: Catholic, Evangelical, and Spiritist.
\item
  Use of relative distribution functions is effectively a multi-scale
  technique, since the intensity of crime can be estimated at different
  distances from various types of places of worship.
\item
  We also used a set of putatively morally neutral commercial
  establishments to serve as controls in our analysis.
\end{enumerate}

Our key findings can be summarized as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Catholic places of worhsip do not seem to geographically project more
  or less of a moral community effect than, say, ice cream shops,
  pharmacies, or supermarkets: the intensity of crime as a function of
  distance to Catholic churches is not significantly different that what
  we observe when we consider distance to any of these types of
  commercial establishments, at any distance.
\item
  The intensity of crime with respect to distance to Evangelical
  churches is more complex than previously known: whereas the intensity
  of crime is higher at relativey short distance from Evangelical places
  of worship, at longer distances it tends to decline even below the
  global intensity of crime and the background level of crime according
  to Socio-Economic Deprivation.
\item
  Spiritist churches are associated with lower intensity of crime at
  very short distance; however, at longer distances(approximately
  between 200 m and 500 m), the intensity of crime is in fact higher
  than the intensity of crime at comparable distances from Catholic and
  Evangelical places of worship, or any of the three kinds of commercial
  establishments.
\end{enumerate}

These results are interesting of and in themselves as they help to
clarify the potential of various types of moral communities to act as
restraints on crime or, on the contrary, as criminogenic factors. They
also suggest several avenues for further research.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  The analysis presented in this paper is to a large extent exploratory.
  For example, to introduce a baseline function in the analysis of
  relative distribution, we used a data reduction technique to obtain an
  indicator of Socio-Economic Deprivation. This indicator was useful to
  determine a general spatial pattern of crime conditional on this
  variable, and to account for a baseline (or background) intensity of
  crime. However, it would be interesting to investigate the effect of
  the individual socio-economic and demographic variables on the
  intensity of crime, as opposed to the aggregated effect of
  Socio-Economic Deprivation. This implies the use of multivariate
  analytical techniques.
\item
  It would be interesting to explore the effect of aggregation on the
  results. On the one hand, this would be informative with respect to
  the well-known issues with aggregation bias in spatial analysis
  (related to the Modifiable Areal Unit Problem in geography; see
  Fotheringham and Wong 1991; Openshaw and Taylor 1979; and Tagashira
  and Okabe 2002). On the other hand, as the results of the research
  presented here, it is possible that analysis at different levels of
  aggregation may tend to capture different spatial and social processes
  of interest.
\item
  And finally, in relation to the latter point, more in-depth research,
  perhaps observational, ethnographic, or participatory studies, could
  help to develop a more refined understanding of the kinds of processes
  that operate at different scales and how they can influence moral
  behavior and crime.
\end{enumerate}

In summary, the research presented on this paper provides information
about the potential of different types of moral communities to reduce
crime, and should be of interest to policy makers as they assess whether
formal or informal forms of social control can be effective to deter
criminal behavior.

@@

@@

@@

\leavevmode\hypertarget{ref-Fotheringham1991modifiable}{}%
Fotheringham, A. S., and D. W. S. Wong. 1991. ``The Modifiable Areal
Unit Problem in Multivariate Statistical-Analysis.'' Journal Article.
\emph{Environment and Planning A} 23 (7): 1025--44.
\url{ISI:A1991GA61200008}.

@@

\leavevmode\hypertarget{ref-Garmany2014space}{}%
Garmany, J. 2014. ``Space for the State? Police, Violence, and Urban
Poverty in Brazil.'' Journal Article. \emph{Annals of the Association of
American Geographers} 104 (6): 1239--55.
\url{https://doi.org/10.1080/00045608.2014.944456}.

@@

\leavevmode\hypertarget{ref-Ichihara2018area}{}%
Ichihara, M. Y. T., D. Ramos, P. Reboucas, F. J. Oliveira, A. J. F.
Ferreira, C. Teixeira, M. Allik, et al. 2018. ``Area Deprivation
Measures Used in Brazil: A Scoping Review.'' Journal Article.
\emph{Revista de Saude Publica} 52 (83): 1--14.
\url{https://doi.org/10.11606/s1518-8787.2018052000933}.

@@

\leavevmode\hypertarget{ref-Openshaw1979million}{}%
Openshaw, S., and P. J. Taylor. 1979. ``A Million or so Correlation
Coefficients: Three Experiments on the Modifiable Areal Unit Problem.''
Book Section. In \emph{Statistical Applications in the Spatial
Sciences}, edited by N. Wrigley, 127--44. London: Pion.

@@

\leavevmode\hypertarget{ref-Tagashira2002modifiable}{}%
Tagashira, N., and A. Okabe. 2002. ``The Modifiable Areal Unit Problem
in a Regression Model Whose Independent Variable Is a Distance from a
Predetermined Point.'' Journal Article. \emph{Geographical Analysis} 34
(1): 1--20. \url{ISI:000173383000001}.
